Structural and Geographic Influences on Residential Parking Availability in Toronto

### 2024-12-01 paper/paper.qmd
added model API description

>>>>

### Model API

This model has been further enhanced by the development of an API that allows users to interact with the Bayesian logistic regression model in a practical and user-friendly manner. The API enables users to input their selected predictor values, such as specific parking types or ward locations, and obtain probabilistic predictions of whether a property is likely to have more than one parking space. This tool bridges the gap between advanced statistical modeling and real-world application, making the findings accessible and actionable for urban planners, policymakers, and other stakeholders.
